---
title: "Precarity"
output: html_notebook
---

```{r}
library(tidyverse)
source("R/street cleaners.R")
source("R/sanitation department.R")
source("R/clean_historic_streets.R")

# map_dfr means take *each* of these years and run "read directory" on them
# sequentially, and then shove them all together into one dataframe.
start_year = 1880
ys = start_year + c(0, 1, 2) |> map_dfr(~read_directory(.x))

y2 = read_directory(1887)
# Probably filter to just home addresses!
y2 |> count(addr_h)
ys = ys |> clean_streets()
ys = ys |> distinct(number, streetname, name, directory_year, occupation)
earlier = ys |> filter(directory_year == start_year)
# middle = ys |> filter(directory_year == start_year + 1)
later = ys |> filter(directory_year == start_year + 2)
```

we can get all possible matches by joining on the frame itself.
```{r}

all_matches = ys |> 
  filter(!is.na(number)) |>
  filter(!is.na(streetname)) |>
  inner_join(ys, by = c("streetname"="streetname", "number" = "number", "name" = "name"))

matches = all_matches |> 
  filter(directory_year.x < directory_year.y)

matches |> count(directory_year.x, directory_year.y)

```

You could also look who's matched in 1881 and 1883 but *not* in 1882 to get
an estimate of the error rate. That seems to be about 15% just missing.

```{r}
unique_not_occupation = matches |> distinct(streetname, number, name, directory_year.x, directory_year.y)

unique_not_occupation |>  filter(directory_year.y == start_year + 3) |>
  inner_join(unique_not_occupation |> filter(directory_year.y == start_year + 2 ), by = c("streetname"="streetname", "number" = "number", "name" = "name"))
  

```

Here's a first stab at matching 1881 to 1883.
```{R}
matches = earlier |> 
  filter(!is.na(number)) |>
  filter(!is.na(streetname)) |>
  inner_join(later, by = c("streetname"="streetname", "number" = "number", "name" = "name"))
```

We can see the matches are working because in places where the address and name 
is constant but the occupation changes, the occupations are very often equivalent.

This actually suggests something interesting, which is that you could look at 
career progressions in this set too. 

```{R}
matches = earlier |> 
  filter(!is.na(number)) |>
  filter(!is.na(streetname)) |>
  inner_join(later, by = c("streetname"="streetname", "number" = "number", "name" = "name")) |>
  count(occupation.x, occupation.y) |>
  filter(occupation.x != occupation.y) |>
  arrange(-n) |> 
  head(30)

```
An easier task is matching on name alone.
```{r}
matches = earlier |> 
  filter(!is.na(number)) |>
  filter(!is.na(streetname)) |>
  inner_join(later, by = c("streetname"="streetname", "name" = "name"))
matches |> filter(number.x != number.y) |>
  count(number.y, number.x) |>
  arrange(-n)


```
Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

